Revenue Maximization for Buyers with Costly Participation

### 2025-02-21 paper/paper.tex
Finish proof of expected revenue

\renewcommand{\Pr}[1]{\mbox{\rm\bf Pr}\left[#1\right]}
\newcommand{\Ex}[1]{\mbox{\rm\bf E}\left[#1\right]}

@@

 \begin{lemma}[\cite{myerson}, Single Buyer]
     Let $\mathcal{M}=(x,p)$ be a truthful single-parameter mechanism, then the expected revenue equals the expected virtual welfare. That is
     \begin{align*}
         \mathbf{E}_v\left[p(v)\right]
         = \mathbf{E}_v\left[x(v)\varphi(v)\right] + p_0
     \end{align*}

@@

@@

 \begin{proof}
    We proof this using a case distinction and drawing the expectation around it.
    First start by fixing $c$ arbitrarily.
    Consider the case that $c > -p_0$. Note that $-p_0$ corresponds to a payment the player would get from the mechanism for participating.
    That means in the case that $c > -p_0$, we do not simply always participate, since our utility could be negative. 
    Therefore we also have $v_x(c) > 0$. 
 \end{proof}

>>>>

\renewcommand{\Pr}[1]{\mbox{\rm\bf Pr}\left[#1\right]}
\newcommand{\Ex}[2][]{\mbox{\rm\bf E}_{#1}\left[#2\right]}
\newcommand{\1}[1]{\mbox{\rm\bf 1}_{#1}}

@@

 \begin{lemma}[\cite{myerson}, Myerson Revenue]
     \label{lemma:myerson-revenue}

     Let $\mathcal{M}=(x,p)$ be a truthful single-parameter mechanism, then the expected revenue equals the expected virtual welfare. That is
     \begin{align*}
         \mathbf{E}_v\left[p(v)\right]
         = \mathbf{E}_v\left[x(v)\varphi(v)\right] + p_0
     \end{align*}

@@

 \begin{align*}
     x_c(v) = \begin{cases}
                  x(v) & v \geq v_x(c)    \\
                  0    & \text{otherwise}
              \end{cases}
 \end{align*}

 Similar the payment rule $p_c(v)$ delegates the the payment rule $p$ in the case that $v \geq v_x(c)$ and otherwise expects no payment.
 Together, they define the mechanism $\mathcal{M}_c = (x_c, p_c)$ induced by the mechanism $\mathcal{M}$.

@@

 \begin{proof}
     We proof this using a case distinction and drawing the expectation around it.
     First start by fixing $c$ arbitrarily.
     Consider the case that $c > -p_0$. Note that $-p_0$ corresponds to a payment the player would get from the mechanism for participating.
     That means in the case that $c > -p_0$, we do not simply always participate, since our utility could be negative. Therefore we also have $v_x(c) > 0$.

     We first consider the case that we partipate, i.e. $v \geq v_x(c)$.
     In that case the payment the player has to pay the payment $p(v)$ of the single parameter mechanism.

     \begin{align}
         \label{eq:payment-participating}
         p_c(v) = p(v) = v x(v) - \int_0^v x(t) dt + p_0
     \end{align}

     We use linearity of the intergral and the definition of utility to express this in terms of the allocation function $x_c$.
     \begin{align*}
         \int_0^v x(t) dt & = \int_0^{v_c(x)} x(t) dt + \int_{v_c(x)}^v x(t) dt     \\
                          & = u^\mathcal{M}(v_c(x)) + p_0 + \int_{v_c(x)}^v x(t) dt \\
                          & = c + p_0 + \int_{v_c(x)}^v x(t) dt
     \end{align*}
     Here the last step uses that $u^\mathcal{M}(v_c(x)) = c$ per definition of $v_c(x)$.

     Plugging this into \autoref{eq:payment-participating} yields
     \begin{align*}
         p_c(v) = v x_c(v) - \int_0^v x_c(t) dt - c
     \end{align*}

     Next we consider the case that the player does not partitipate, i.e. $v < v_x(c)$.
     In that case, the payment rule requests no payment, i.e. $p_c(v) = 0$, yet conveniently some part of the expression found before are also $0$:

     \begin{align*}
         p_c(v) = 0 = v x_c(v) - \int_0^v x_c(t) dt
     \end{align*}

     Thus we can represent this entire case using an inditcator function:
     \begin{align*}
         p_c(v) = 0 = v x_c(v) - \int_0^v x_c(t) dt - c \1{v \geq v_x(c)}
     \end{align*}

     Drawing the expectation around the value $v \sim \bar{F}_c$ while keeping the participation cost still fixed yields

     \begin{align*}
         \Ex[v \sim \bar{F}_c]{p_c(v)} & = \Ex[v \sim \bar{F}_c]{v x_c(v) - \int_0^v x_c(t) dt - c \1{v \geq v_x(c)}}   \\
                                       & = \Ex[v \sim \bar{F}_c]{v x_c(v) - \int_0^v x_c(t) dt} - \Pr{v \geq v_x(c)}c   \\
                                       & = \Ex[v \sim \bar{F}_c]{x_c(v) \varphi_c(v)} - (1 - \bar{F}_c(v_x(c))) \cdot c \\
     \end{align*}

     Here in the last step we used that for fixed $c$, $M_c$ is a thruthful mechanism thus we can apply \autoref{lemma:myerson-revenue} and we also used the cumulative distribution.

     Now we consider the opposite case, that is that $c \leq -p_0$.
     Analogously to the case before, $c \leq -p_0$ means that the mechanism's payment for simply participating already pays of our participation cost.
     Certainly in that case $v_x(c) = 0$.

     Therefore the player always participates and pays $p(v)$. In the case that $v_x(c) = 0$, we have $x_c(v) = x(v)$ for all $v \in \RR_{\geq 0}$, therefore:
     \begin{align*}
         p_c(v) = p(v) = v x(v) - \int_0^v x(t)dt + p_0 = v x_c(v) - \int_0^v x_c(t)dt + p_0
     \end{align*}

     Drawing again the expectation around the value $v \sim \bar{F}_c$ while keeping the participation cost still fixed yields

     \begin{align*}
         \Ex[v \sim \bar{F}_c]{p_c(v)} & = \Ex[v \sim \bar{F}_c]{v x_c(v) - \int_0^v x_c(t)dt + p_0}                  \\
                                       & = \Ex[v \sim \bar{F}_c]{x_c(v) \varphi_c(v)} + p_0                           \\
                                       & = \Ex[v \sim \bar{F}_c]{x_c(v) \varphi_c(v)} + (1 - \bar{F}_{c}(v_x(c))) p_0
     \end{align*}

     Where in the last equality, we used that since $v_x(c) = 0$, $\bar{F}_{c}(v_x(c)) = 0$ as well.

     Now we can finally draw the expectation around the previously fixed $c$ and get to the wished theorem:

     \begin{align*}
         \Ex{p_c(v)} & = \Ex[c \sim G]{\Ex[v \sim \bar{F}_c]{x_c(v) \varphi_c(v)} + (1 - \bar{F}_{c}(v_x(c))) \max\{c, -p_0\} }
     \end{align*}
 \end{proof}
